New Approaches to Uniform Boosting

### 2014-08-21 assets/paperdraft/paper_draft.tex
Corrected according to JINST styles

\documentclass[12pt]{article}

% AMS packages:
\usepackage{amsmath, amsthm, amsfonts}
\usepackage[margin=0.5in]{geometry}

@@

%-----------------------------------------------------------------
\title{New Approaches to Uniform Boosting }
\author{
}

@@

% \abstract{Abstract goes here}

@@

\subsection{Distribution Similarity Approach}
\label{subsection:similarity}

@@

Let's use the metrics introduces in the section \ref{subsection:similarity}:
\[
	\sum_{\bin} \binweight \int \abs{F_{\bin}(x) - F(x)}^p dF(x),
\]
which is good as a measure, but due to the non-smoothness of $F(x)$ it's 
gradient is singular, so we use instead
\[
	\FL = \sum_{\bin} \binweight \int \abs{F_{\bin}(x) - F(x)}^p dx.
\]

@@

\section{Acknowledgments}

@@

The code for classifiers ans links to final notebooks with results in the article.

\begin{thebibliography}{99}

\bibitem{Cd94} Author, \emph{Title}, Journal/Editor, (year)

>>>>

\pdfoutput=1 % only if pdf/png/jpg images are used
\documentclass{JINST}

\title{New Approaches to Uniform Boosting}

\author{
Aleksandar Bukva, 
Vladimir Gligorov$^d$,
Alex Rogozhnikov$^{a,b}$\thanks{Corresponding author.}~ ,
Andrey Ustuzhanin$^b$ and
Mike Williams$^c$\\
\llap{$^a$}Lomonosov Moscow State University, Moscow, Russia\\
\llap{$^b$}Yandex LLC, Moscow, Russia\\
\llap{$^c$}Massachusetts Institute of Technology, Cambridge, MA, United States \\
\llap{$^d$}Organisation Européenne pour la Recherche Nucléaire (CERN), Geneva \\Switzerland 
E-mail: \email{alex.rogozhnikov@yandex.ru}}

\abstract{
% Abstract must be short enough to appear in this page together with title, authors, their addresses and keywords.
The use of multivariate classifiers has become commonplace in particle physics. 
Typically, a series of classifiers is trained rather than just one to enhance the performance; this is known as boosting.

In some applications of high energy physics (i.e., amplitude analyses) 
classifiers should not only optimize some integrated figure of merit, but produce a uniform selection efficiency in a space of selected physical variables.
Recently uBoost technique of boosting was proposed which addresses this issue.

In this paper we introduce several approaches to measure the uniformity of efficiency and propose new boosting techniques.
}

% AMS packages:
\usepackage{amsmath, amsthm, amsfonts}

@@

%-----------------------------------------------------------------

@@

@@

\subsection{Distribution Similarity Approach}
\label{sec:similarity}

@@

Let's use the metrics introduces in the section \ref{sec:similarity}:
\[
	\sum_{\bin} \binweight \int \abs{F_{\bin}(x) - F(x)}^p dF(x),
\]
which is good as a measure, but due to the non-smoothness of $F(x)$ it's 
gradient is singular, so we use instead
\[
	\FL = \sum_{\bin} \binweight \int \abs{F_{\bin}(x) - F(x)}^p dx.
\]

@@

@@

The link on the repository ans links to final notebooks with results in the article.

\acknowledgments

\begin{thebibliography}{9}

\bibitem{bib1}
Authors,
\emph{Title},
\emph{J. Ref.} \textbf{vol} (year) page.

\bibitem{bib2}
A. Pietropaolo et al., \emph{DINS measurements on VESUVIO in the
    resonance detector configuration: proton mean kinetic energy in
    water}, \jinst{1}{2006}{P04001}.

\bibitem{bib3}
A.I. Harris,
\emph{Spectroscopy with multichannel correlation radiometers},
\href{http://dx.doi.org/10.1063/1.1898643}
{\emph{Rev.\ Sci.\ Instrum.} {\bf 76} (2005) 054503}
[\astroph{0504449}].

\bibitem{bib4}
G.F. Knoll, \emph{Radiation detection and measurements}, John Wiley
    and Sons, Inc., New York 2000.

\bibitem{bib5}
V. Dangendorf, \emph{Time-resolved fast-neutron imaging with a
pulse-counting image intensifier}, in proceedings of
\emph{International workshop on fast neutron detectors and
applications}, April, 3--6, 2006 University of Cape Town, South Africa
\pos{PoS(FNDA2006)008}.
